Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-19 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables,
      rstatix,
      MBESS)

@@

>>>>

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables,
      rstatix)

@@

### OVERALL SCORE (All)
# Boxplot showing outliers (All)
ggplot(df_sjt_mean, aes(x = "", y = All)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of SJT (All)",
       y = "Overall score") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_sjt_mean$All, 0.25)
Q3 <- quantile(df_sjt_mean$All, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_sjt_all <- df_sjt_mean %>%
  filter(All >= LowerBound & All <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_sjt_mean)  # Original data
nrow(df_no_outliers_sjt_all)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_sjt_all <- df_sjt_mean %>%
  filter(All < LowerBound | All > UpperBound)

# View the removed outliers
df_outliers_sjt_all

### MANAGING MOMENTUM
# Boxplot showing outliers (All)
ggplot(df_sjt_mean, aes(x = "", y = `Managing momentum`)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of SJT (Managing Momentum)",
       y = "Score") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_sjt_mean$`Managing momentum`, 0.25)
Q3 <- quantile(df_sjt_mean$`Managing momentum`, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_sjt_mm <- df_sjt_mean %>%
  filter(`Managing momentum` >= LowerBound & `Managing momentum` <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_sjt_mean)  # Original data
nrow(df_no_outliers_sjt_mm)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_sjt_mm <- df_sjt_mean %>%
  filter(`Managing momentum` < LowerBound | `Managing momentum` > UpperBound)

# View the removed outliers
df_outliers_sjt_mm

### MONITORING
# Boxplot showing outliers (All)
ggplot(df_sjt_mean, aes(x = "", y = Monitoring)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of SJT (Monitoring)",
       y = "Score") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_sjt_mean$Monitoring, 0.25)
Q3 <- quantile(df_sjt_mean$Monitoring, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_sjt_m <- df_sjt_mean %>%
  filter(Monitoring >= LowerBound & Monitoring <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_sjt_mean)  # Original data
nrow(df_no_outliers_sjt_m)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_sjt_m <- df_sjt_mean %>%
  filter(Monitoring < LowerBound | Monitoring > UpperBound)

# View the removed outliers
df_outliers_sjt_m

### RULES & ROUTINES
# Boxplot showing outliers (All)
ggplot(df_sjt_mean, aes(x = "", y = `Rules and routines`)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of SJT (Rules & routines)",
       y = "Score") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_sjt_mean$`Rules and routines`, 0.25)
Q3 <- quantile(df_sjt_mean$`Rules and routines`, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_sjt_r <- df_sjt_mean %>%
  filter(`Rules and routines` >= LowerBound & `Rules and routines` <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_sjt_mean)  # Original data
nrow(df_no_outliers_sjt_r)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_sjt_r <- df_sjt_mean %>%
  filter(`Rules and routines` < LowerBound | `Rules and routines` > UpperBound)

# View the removed outliers
df_outliers_sjt_r
